% =====================================================================
%  Nikhil Gangaramani — AI Engineer — Curriculum Vitae
%  Compile: pdflatex nikhil_gangaramani_cv.tex
%  This file is also served verbatim by the portfolio's ⌘K palette
%  ("fetch cv"). Content mirrors src/data/profile.ts.
% =====================================================================
\documentclass[10pt,a4paper]{article}

\usepackage[margin=1.6cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=1pt, topsep=2pt}
\pagestyle{empty}

\begin{document}

% ---------------------------------------------------------------------
\begin{center}
  {\LARGE\bfseries Nikhil Gangaramani}\\[2pt]
  AI Engineer --- RAG Systems \& High-Throughput Data Pipelines\\[2pt]
  Mumbai, IN \; | \;
  \href{mailto:gangaramaninikhil@gmail.com}{gangaramaninikhil@gmail.com} \; | \;
  \href{https://github.com/gangaramani-nikhil}{github.com/gangaramani-nikhil}
\end{center}

% ---------------------------------------------------------------------
\section{Summary}
AI engineer focused on production-grade retrieval systems and the data
infrastructure underneath them: RAG pipelines over SEC filings,
ingestion/routing layers moving 40--100M data points per day, and query
layers rebuilt for speed (+75\% on Simfund/MarketPulse). Comfortable owning
systems end-to-end --- from chunking strategy and vector-index hygiene to
Kafka partitioning and PostgreSQL query plans.

% ---------------------------------------------------------------------
\section{Experience}
\textbf{Institutional Shareholder Services (ISS)} \hfill 2023 --- Present\\
\textit{Software Engineer --- Data \& AI \hfill Simfund (MarketPulse)}
\begin{itemize}
  \item Rebuilt the hot query path on the Simfund (MarketPulse)
        fund-analytics platform --- covering indexes, denormalized read
        models, and aggregate pushdown --- for a \textbf{+75\% query
        performance increase}.
  \item Built Golang ingestion services handling tens of millions of market
        data points daily with strict ordering and idempotency guarantees.
  \item Shipped RAG tooling over SEC filings so analysts query institutional
        holdings in natural language instead of SQL.
\end{itemize}

\textbf{Backend Platform Work} \hfill 2022 --- 2023\\
\textit{Software Engineer \hfill JVM Services}
\begin{itemize}
  \item Owned latency-sensitive Java services; profiled allocation pressure
        and tuned generational GC to cut p99 pauses.
  \item Introduced structured concurrency and load-shedding so services
        degrade predictably under burst load.
\end{itemize}

% ---------------------------------------------------------------------
\section{Projects}
\textbf{MI Buddy} --- RAG over SEC 13F institutional filings
\begin{itemize}
  \item Parse $\rightarrow$ chunk $\rightarrow$ embed $\rightarrow$
        retrieve/rerank pipeline; streamed answers with citations back into
        the source filing. (Python, pgvector, FastAPI, LLM APIs)
\end{itemize}
\textbf{High-Throughput Routing} --- 40--100M data points/day
\begin{itemize}
  \item Golang worker pools fanning Kafka partitions through a rules-based
        router; backpressure + dead-letter handling; at-least-once delivery
        into idempotent sinks.
\end{itemize}

% ---------------------------------------------------------------------
\section{Skills}
\textbf{Languages:} Golang, Python, Java, TypeScript, SQL\\
\textbf{AI/Retrieval:} RAG architecture, embeddings, pgvector/FAISS,
LLM orchestration \& evals\\
\textbf{Data/Infra:} Kafka, PostgreSQL, Redis, Docker/Kubernetes, AWS

\end{document}
